Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-03 paper/galsize_paper.tex
Finished discussion of figure 3 in results section

>>>>

In the $\mstar-$only model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies. Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.

Much more successful is the profile co-evolution model shown with the solid curves in Figure \ref{fig:clustering_ratio_upshot}. The strongly negative clustering ratios predicted by the assumption of profile co-evolution can be understood in terms of the same features discussed above. Figure \ref{fig:coevolutionmodel} shows that at fixed $\mpeak,$ larger galaxies will occupy halos with larger $\rspeak.$ Since halo concentration $c=\rvir/R_{\rm s},$ this implies that high-concentration galaxies will tend to host smaller galaxies. Both satellites and splashback centrals have higher concentration than true centrals, another manifestation of assembly bias, and so the assumption of profile co-evolution naturally results in an enhancement of the clustering ratios beyond the $\rvir-$only model.
